Automated topic naming to support cross-project analysis of software maintenance activities

### 2011-03-24 msr/msr2011.tex
finalish conclusion edit
Can we apply to bug reports? Why versus how?     - [X] The question that needs to be better answered is what           application this technique has to commit messages?           - If it is only workable on commit messages, is it limited           to providing coarse comparisons of the past history of           projects?           - response: answered in discussion section. No it isn't             limited but we didn't test it.     - [X] - Are the commit messages close enough to bug report titles           that the approach might work on bug reports as well?

%One challenge for software maintenance is to identify the reasons
%behind software development activities. 
%Identifying these reasons provides insight into \emph{why} certain
%changes were made. 
%migod
A key problem for practising software maintainers is gaining an understanding of \emph{why} a system has evolved the way it has. Looking back on streams of artifacts scattered across different repositories, inferring what activities were performed, when, and for what reasons, is hard to do without expert advice from the developers involved. In this work we seek to provide automated help in labelling development topics that have been extracted from commit logs.

@@

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
%\todo[inline]{more on intro ... why should the reader care about
 % this. It needs to show how the stuff in the intro (applications) is
 % possible}
%%% XXX NEIL I don't get this.. VVVVV
%\todo[inline]{fix section headings}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has. 
In this section we demonstrate the value of labelled topic extraction in addressing this issue. 
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with two research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR was of more interest at one point in the life-cycle than another, this suggests that development activity shifted focus. For example, if a developer expected to see a recent focus on \emph{reliability}, but instead \emph{usability} dominated, he or she might re-prioritize up-coming work items.
\item \emph{Do projects differ in their relative interest in NFRs?} A program manager would be interested in knowing whether a particular NFR, such as \emph{reliability}, was more important for one project than another. This could be to confirm the initial design goals, or to track the progress on that quarter's objectives.  
\end{enumerate}

@@

>>>>

%One challenge for software maintenance is to identify the reasons
%behind software development activities. 
%Identifying these reasons provides insight into \emph{why} certain
%changes were made. 
%migod
A key problem for practising software maintainers is gaining an
understanding of \emph{why} a system has evolved the way it has. 
Looking back on streams of artifacts scattered across different
repositories, inferring what activities were performed, when, and for
what reasons, is hard to do without expert advice from the developers
involved. 
%new stuff
% edit this. awkward
This is different than \emph{how}, because the behaviour of change itself is the
how, not the \emph{why}
In this work we seek to provide automated help in labelling development topics that have been extracted from commit logs.

@@

\section{Understanding software maintenance activities} 
\label{sec:analysis}
% \todo[inline]{talk about this topic in one section}
% \todo[inline]{reference project name Nomen more}
%In order to test  our ROC values produced acceptable results, we now turn to
%\emph{applying} those techniques to understand software maintenance
%activities. 
%\todo[inline]{more on intro ... why should the reader care about
 % this. It needs to show how the stuff in the intro (applications) is
 % possible}
%%% XXX NEIL I don't get this.. VVVVV
%\todo[inline]{fix section headings}
As we mentioned in the introduction, a key issue in software maintenance is understanding \emph{why} a system has evolved the way it has. 
In this section we demonstrate the value of labelled topic extraction
in addressing this issue. 
% more why
Labelled topics address \emph{why}  because they show why changes
occurred rather than \emph{how}. 
The \emph{how} of a change is the change itself, the purpose or
\emph{why} is what we are after.
We investigate the history of the two large-scale database systems that we studied. 
We use our technique to show the topic of development efforts over time in each project.
%We evaluated two research questions using the ground truth data that we annotated by hand:
We motivated our investigation with two research questions:
\begin{enumerate}
\item \emph{Do NFR frequencies change over time?} If a particular NFR was of more interest at one point in the life-cycle than another, this suggests that development activity shifted focus. For example, if a developer expected to see a recent focus on \emph{reliability}, but instead \emph{usability} dominated, he or she might re-prioritize up-coming work items.
\item \emph{Do projects differ in their relative interest in NFRs?} A program manager would be interested in knowing whether a particular NFR, such as \emph{reliability}, was more important for one project than another. This could be to confirm the initial design goals, or to track the progress on that quarter's objectives.  
\end{enumerate}

@@

Since this work focuses on labelling natural language commit log
comments we feel it can adapted to other natural language artifacts
such as mailing-list discussions and bug reports, even though that was
not evaluated in this paper. Bug reports might not exhibit the same
behaviour as commits in terms of dominant topics.
